Thermodynamic response functions in a cell fluid model

### 2024-08-11 main_morse_response_functions.tex
add fourier transform for repulsive part of interaction potential

	\section{The interaction potential}
	The potential of interaction between particles is taken in a form of a modified Morse potential
	\begin{equation}
		\label{def:mod_morse}
		U(r) = C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
	\end{equation}
	where $R_0$ is the coordinate of the potential minimum, $\alpha$ is an effective range of interaction, $\gamma$ and $n_0$ are parameters of the model. Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
	\begin{equation}
		C_{H} = \frac{\varepsilon n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
	\end{equation}
	where $\varepsilon$ is the depth of the potential well at $r=R_0$. This potential is reduced to the ordinary Morse potential~\cite{Morse1929} at $\gamma=2$. For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~\cite{KozlovskiiDobush2020}.

@@

	\section{The equation of state}
	The equation of state obtained in~\cite{KozlovskiiDobush2020} reads
	\begin{equation}
		\label{eq:eosMT}
		Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
	\end{equation}
	The quantities in the left-hand side of the equation are $P$, the pressure; $\beta$, the inverse temperature; $v$, cell volume. The quantities in the right-hand side are, in general, functions of the temperature $T$ and the chemical potential $\mu$. Let us present their expressions explicitly.

@@

	The quantity $W(0)$ is expressed via parameters of the potential~(\ref{def:mod_morse}) as follows
	\begin{equation}
	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right],
	\end{equation}
	where
	\begin{align} 
		& B = 2 \gamma^3 e^{(1-\gamma)/\alpha},\nonumber \\
		& A_\gamma = A e^{(n_0-\gamma)/\alpha} \left( \gamma / n_0\right)^3,
	\end{align}
	and $\Phi^{(r)}(0)$ is the Fourier transform of the repulsive part of the potential at $\abs{\vb k}=0$. The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a term in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$.

	The coefficients $g_n$ are given by the formulas:
	\begin{align}
		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, 
	\end{align}
	where $T_n(p,\alpha^*)$ are the following special functions
	\begin{equation}
	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
	\end{equation}
	Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
	\begin{equation}
	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
	\end{equation} 
	The quantity $\beta_c$ denotes the critical value of the inverse temperature.
	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature. The numerical values for other coefficients used in this paper are the same as those in~\cite{KozlovskiiDobush2020}:
	\begin{equation*}
		\alpha^* = 5.0, \quad \gamma = 1.65, \quad n_0 = 1.521.
	\end{equation*}

>>>>

	\section{The interaction potential}
	The potential of interaction between particles is taken in a form of a modified Morse potential
	\begin{equation}
		\label{def:mod_morse}
		U(r) = \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
	\end{equation}
	where $R_0$ is the coordinate of the potential minimum, $\alpha$ is an effective range of interaction, $\gamma$ and $n_0$ are parameters of the model. Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
	\begin{equation}
		C_{H} = \frac{n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
	\end{equation}
	where $\varepsilon$ is the depth of the potential well at $r=R_0$. This potential is reduced to the ordinary Morse potential~\cite{Morse1929} at $\gamma=2$. For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~\cite{KozlovskiiDobush2020}.

@@

	\section{The equation of state}
	The equation of state obtained in~\cite[see Eq.(42)]{KozlovskiiDobush2020} reads
	\begin{equation}
		\label{eq:eosMT}
		Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
	\end{equation}
	The quantities in the left-hand side of the equation are $P$, the pressure; $\beta$, the inverse temperature; $v$, cell volume. The quantities in the right-hand side are, in general, functions of the temperature $T$ and the chemical potential $\mu$. Let us present their expressions explicitly.

@@

	The quantity $W(0)$ is expressed via parameters of the potential~(\ref{def:mod_morse}) as follows
	\begin{equation}
	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right],
	\end{equation}
	where
	\begin{align*} 
		& B = 2 \gamma^3 e^{(1-\gamma)R_0/\alpha},
		\nonumber \\
		& A_\gamma = A e^{(n_0-\gamma)R_0/\alpha} \left( \gamma / n_0\right)^3, 
	\end{align*}
	and $\Phi^{(r)}(0)$ is the Fourier transform of the repulsive part of the potential at $\abs{\vb k}=0$
	\begin{equation*}
		\Phi^{(r)}(0) = \varepsilon C_H 8\pi {\rm e}^{\gamma R_0/\alpha} \left(\frac{\alpha}{\gamma}\right)^3.
	\end{equation*}

	The parameter $\chi_0$ is used in~\cite{KozlovskiiDobush2020} to single out a contribution in the Fourier transform of the potential that is treated as a reference system defined in the reciprocal space, and is selected as $\chi_0 = 0.07$~\cite[see Eq.(24)]{KozlovskiiDobush2020}.

	The coefficients $g_n$ are given by the formulas:
	\begin{align}
		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2, 
	\end{align}
	where $T_n(p,\alpha^*)$ are the following special functions
	\begin{equation}
	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
	\end{equation}
	Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
	\begin{equation}
	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
	\end{equation} 
	The quantity $\beta_c$ denotes the critical value of the inverse temperature.
	Since $p$ is independent of temperature, the coefficients $g_n$ are also independent of temperature. The numerical values for other coefficients used in this paper are the same as those in~\cite[see Eqs.(5), (23), and (24)]{KozlovskiiDobush2020}:
	\begin{eqnarray*}
		\alpha^* = 5.0, & \quad \gamma = 1.65, \\
		n_0 = 1.521, & \quad R_0/\alpha = 2.9544, \\
		\chi_0 = 0.07.
	\end{eqnarray*}
